troubleshooting

### 2024-04-26 README.Rmd
made changes in the data that is retained to allow for the development of different parsers for outputs from different software

# msp-ms

@@

**Making mspms generically useful**.

1. *calculate_all_cleavages()*: Calculates all possible cleavages for peptide library sequences.

**Data Proessing/ Normalization**.

1. *prepare_for_normalyzer()*:Takes two input files from PEAKS and combines them.    
2. *normalyze()*: Normalizes values and then does a reverse log2 transformation.    
3. *handle_outliers()*: Looks for outliers across replicates. Removes them.     
4. *impute()*: Imputes data for missing values (not including NAs introduced by handle_outliers()).    
5. *join_with_library()*: Joins the normalyzed data with the peptide library sequences.  
6. *add_cleavages()*: Figures out the locations of the detected clevages within the library of peptide sequences used. Is it cleaved at the N or C terminus, or both?  Uses *cterm_cleavage()* and *nterm_cleavage()* to do this.  
7. *polish()*: combines the cleavage info into one column. Discards peptides that were cleaved on both sides or not at all.  
8. *prepare_for_stats()*: Reshapes the data into a long format and appends the data in the design matrix to make statistical testing easy to perform.

@@

## Making Generically Usefull

@@

### Combining Peaks file outputs

# Prepare the data for normalyzer analysis
prepared_data = prepare_for_normalyzer(lfq_filename,id_filename)

@@

```{r}
test_seq = readLines("tests/cleavage_seq_test.txt")

mspms::plot_cleavage_motif(test_seq,background_universe)
```

>>>>

# mspms

@@

**Making mspms generically useful**.   
1. *prepare_peaks()*:Takes two input files from PEAKS and combines them. 
2. *prepare_pd()*: prepares exported files from proteome discoverer.  
  - *extract_design_matrix_pd()*: Extracts the design matrix from the proteome discoverer file.  
3. *prepare_spectronaut()*: prepares exported files from spectronaut - note in development, not yet implemented.  
4. *calculate_all_cleavages()*: Calculates all possible cleavages for peptide library sequences.

**Data Proessing/ Normalization**. 
1. *normalyze()*: Normalizes values and then does a reverse log2 transformation.    
2. *handle_outliers()*: Looks for outliers across replicates. Removes them.     
3. *impute()*: Imputes data for missing values (not including NAs introduced by handle_outliers()).    
4. *join_with_library()*: Joins the normalyzed data with the peptide library sequences.  
5. *add_cleavages()*: Figures out the locations of the detected clevages within the library of peptide sequences used. Is it cleaved at the N or C terminus, or both?  Uses *cterm_cleavage()* and *nterm_cleavage()* to do this.  
6. *polish()*: combines the cleavage info into one column. Discards peptides that were cleaved on both sides or not at all.  
7. *prepare_for_stats()*: Reshapes the data into a long format and appends the data in the design matrix to make statistical testing easy to perform.

@@

## Making Generically Usefull.

### Formating Peaks File Outputs.

# Prepare the data for normalyzer analysis
prepared_data = prepare_peaks(lfq_filename,id_filename)

@@

@@
